Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-01-16 analyses/reproduce_analyses.Rmd
I'm now happy with the aesthetics of the reproducible analyses.

Read in data, packages, and required functions.

```{r read data and functions, results='hide'}
# Load required libraries
library(car)        # for homogeneity of variance test
library(tidyverse)  # for managing data
library(cowplot)    # pretty default ggplots
library(broom)      # for tidying multiple linear models
library(viridis)    # for color palette
library(lme4)       # for generalized linear mixed models
library(latex2exp)  # using Latex notation for axes labels
library(stringr)
library(MVN)        # assessing multivariate normality assumption

# Load and manage data

  # subset data for analysis
  filter(egg.ptoid > 0 | larval.ptoid > 0 | pupa > 0) %>% # eliminate unknown sources of mortality
  filter(Treatment == "Ectoparasitoid exclusion" & larval.ptoid < 1 | Treatment == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  mutate(Foodweb = ifelse(Treatment=="Control","Complex","Simple"),
         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg.ptoid = as.numeric(ifelse(egg.ptoid > 0, 1, 0)), # there were a couple occassions where two egg parasitoids were found in a single chamber. I set these to 1 to permit an analysis with a binomial model.
         # transform and scale traits to approximate multivariate normal assumption
         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))))

# Custom functions and parameters to avoid repetitive code

# Transform logit to probability
inverse_logit <- function(x) exp(x)/(1+exp(x))

@@

  # Organize data
  return(list(absolute_fitness = absolute_fitness_df, relative_fitness = relative_fitness_df))
}

# Number of bootstrap replicates
n_boots_analysis <- 100
n_boots_plots <- 100

# Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/; order -> orange, light blue, green, yellow, dark blue, red, pink
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
complex_color <- cbPalette[6] 
simple_color <- cbPalette[5] 
treatment_colors <- c(complex_color, simple_color)

@@

```{r Egg-Parasitoid-Selection, include=FALSE, eval=FALSE}
# this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.
eggegg_RF_Pref <- bootstrap_fitness(
  logistic_model = eggegg_model, 
  newdata = newdata_Pref,
  bootstraps=n_boots_plots)

>>>>

Load required libraries.

```{r required libraries, results='hide'}
library(car)        # for homogeneity of variance test
library(tidyverse)  # for managing data
library(cowplot)    # pretty default ggplots
library(broom)      # for tidying multiple linear models
library(viridis)    # for color palette
library(lme4)       # for generalized linear mixed models
library(latex2exp)  # using Latex notation for axes labels
library(stringr)
library(MVN)        # assessing multivariate normality assumption
```

Write custom functions to avoid repetitive code.

```{r custom functions}
# Transform logit to probability
inverse_logit <- function(x) exp(x)/(1+exp(x))

@@

  # Organize data
  return(list(absolute_fitness = absolute_fitness_df, relative_fitness = relative_fitness_df))
}
```

Set parameters for analyses and plots.

```{r set parameters}
# Number of bootstrap replicates
n_boots_analysis <- 100
n_boots_plots <- 100

# Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/; 
# order: orange, light blue, green, yellow, dark blue, red, pink
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
complex_color <- cbPalette[6] 
simple_color <- cbPalette[5] 
treatment_colors <- c(complex_color, simple_color)
```

Read and tidy data for analyses.

```{r read and tidy data}

  # eliminate unknown sources of mortality
  filter(egg.ptoid > 0 | larval.ptoid > 0 | pupa > 0) %>% 
  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  filter(Treatment == "Ectoparasitoid exclusion" & larval.ptoid < 1 | Treatment == "Control") %>% 
  mutate(Foodweb = ifelse(Treatment=="Control","Complex","Simple"), # rename Treatment to match presentation in manuscript
         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg.ptoid = as.numeric(ifelse(egg.ptoid > 0, 1, 0)), # there were a couple occassions where two egg parasitoids were found in a single chamber. I set these to 1 to permit an analysis with a binomial model.

         # transform and scale traits to approximate multivariate normal assumption
         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))))

@@

```{r Egg-Parasitoid-Selection, fig.cap="Selection on extended phenotype (oviposition preference) of egg parasitoids"}
# this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.
eggegg_RF_Pref <- bootstrap_fitness(
  logistic_model = eggegg_model, 
  newdata = newdata_Pref,
  bootstraps=n_boots_plots)
